A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-11 sections/05-responses.tex
Change author order, make sure tables are next to figures.
Fixing typo
Removing 'Likert-like' and using just 'scale'

@@

\begin{table}[htpb]
    \centering
    \begin{tabular}{@{}p{0.9\columnwidth}p{0.08\columnwidth}@{}}
        \toprule
        \multicolumn{1}{c}{\scriptsize{Have you$\dots$}} & \textnumero \\ \midrule
        \scriptsize{Had contact with parallel and distributed concepts before?} & $(1)$ \\
        \scriptsize{Had contat with the APIs before?} & $(2)$ \\
        \scriptsize{Learned from the OpenMP class?} & $(3)$ \\
        \scriptsize{Learned from the Pthreads class?} & $(4)$ \\ \bottomrule
    \end{tabular}
    \caption{Questions for Figure \ref{fig:classes}}
    \label{tab:classes}
    \vspace{-0.6cm}
\end{table}

@@

We asked the students to answer 3 sets of questions regarding their
experience with \textit{OpenMP} and \textit{Pthreads}, \textit{after}
completing the assignment.
The first set of questions used a Likert-type Scale to measure the relationship
of the students with the two APIs in the context of the assignment. The Likert
Scale~\cite{likert1932technique} enables respondents to express their agreement
or disagreement with specific statements. Respondents choose between five
options: \textit{Strongly Agree} (SA), \textit{Agree} (A), \textit{Neutral}
(N), \textit{Disagree} (D) and \textit{Strongly Disagree}.

@@

\begin{table}[htpb]
    \centering
    \begin{tabular}{@{}p{0.7\columnwidth}p{0.1\columnwidth}p{0.05\columnwidth}@{}}
        \toprule
        \multicolumn{2}{c}{\scriptsize{It is easy to$\dots$}} & \textnumero \\ \midrule
        \multirow{2}{*}{\parbox{0.7\columnwidth}{\scriptsize{Parallelize loops with independent iterations using:}}} & \scriptsize{OpenMP} & $(1)$ \\
        & \scriptsize{Pthreads} & $(2)$ \\
        \addlinespace{}
        \multirow{2}{*}{\parbox{0.7\columnwidth}{\scriptsize{Parallelize nested loops with independent iterations using:}}} & \scriptsize{OpenMP} & $(3)$ \\
        &  \scriptsize{Pthreads} & $(4)$ \\
        \addlinespace{}
        \multirow{2}{*}{\parbox{0.7\columnwidth}{\scriptsize{Improve the performance of sequential code using:}}} & \scriptsize{OpenMP} & $(5)$  \\
        &  \scriptsize{Pthreads} & $(6)$ \\ \bottomrule
    \end{tabular}
    \caption{Likert-like Scale questions for Figure \ref{fig:likert}}
    \label{tab:likert}
    \vspace{-0.6em}
\end{table}

\begin{figure}[htpb]
    \vspace{-2em}
    \centering
    \includegraphics[width=0.85\columnwidth]{likert_questions}
    \caption{Students' responses to the Likert Scale questions in Table \ref{tab:likert}}
    \label{fig:likert}
    \vspace{-1em}
\end{figure}

Figure \ref{fig:likert} shows a visualization of the students' responses.  The
height of each stacked sub-column represents the percentage of respondents that
selected each of the correspondent Likert scale agreement levels, which are
represented by different colors.

@@

>>>>

\begin{table}[htpb]
    \centering
    \begin{tabular}{@{}p{0.9\columnwidth}p{0.08\columnwidth}@{}}
        \toprule
        \multicolumn{1}{c}{\scriptsize{Have you$\dots$}} & \textnumero \\ \midrule
        \scriptsize{Had contact with parallel and distributed concepts before?} & $(1)$ \\
        \scriptsize{Had contact with the APIs before?} & $(2)$ \\
        \scriptsize{Learned from the OpenMP class?} & $(3)$ \\
        \scriptsize{Learned from the Pthreads class?} & $(4)$ \\ \bottomrule
    \end{tabular}
    \caption{Questions for Figure \ref{fig:classes}}
    \label{tab:classes}
    \vspace{-0.6cm}
\end{table}

@@

@@

We asked the students to answer 3 sets of questions regarding their
experience with \textit{OpenMP} and \textit{Pthreads}, \textit{after}
completing the assignment.
The first set of questions used a scale defined by us with 5 levels to measure the relationship
of the students with the two APIs in the context of the assignment. This kind of scale enables respondents to express their agreement
or disagreement with specific statements~\cite{likert1932technique}. Respondents choose between five
options: \textit{Strongly Agree} (SA), \textit{Agree} (A), \textit{Neutral}
(N), \textit{Disagree} (D) and \textit{Strongly Disagree}.

@@

Figure \ref{fig:likert} shows a visualization of the students' responses.  The
height of each stacked sub-column represents the percentage of respondents that
selected each of the correspondent scale agreement levels, which are
represented by different colors.

@@

\begin{table}[htpb]
    \centering
    \begin{tabular}{@{}p{0.7\columnwidth}p{0.1\columnwidth}p{0.05\columnwidth}@{}}
        \toprule
        \multicolumn{2}{c}{\scriptsize{It is easy to$\dots$}} & \textnumero \\ \midrule
        \multirow{2}{*}{\parbox{0.7\columnwidth}{\scriptsize{Parallelize loops with independent iterations using:}}} & \scriptsize{OpenMP} & $(1)$ \\
        & \scriptsize{Pthreads} & $(2)$ \\
        \addlinespace{}
        \multirow{2}{*}{\parbox{0.7\columnwidth}{\scriptsize{Parallelize nested loops with independent iterations using:}}} & \scriptsize{OpenMP} & $(3)$ \\
        &  \scriptsize{Pthreads} & $(4)$ \\
        \addlinespace{}
        \multirow{2}{*}{\parbox{0.7\columnwidth}{\scriptsize{Improve the performance of sequential code using:}}} & \scriptsize{OpenMP} & $(5)$  \\
        &  \scriptsize{Pthreads} & $(6)$ \\ \bottomrule
    \end{tabular}
    \caption{Scale questions for Figure \ref{fig:likert}}
    \label{tab:likert}
    \vspace{-0.6em}
\end{table}

\begin{figure}[htpb]
    \vspace{-2em}
    \centering
    \includegraphics[width=0.85\columnwidth]{likert_questions}
    \caption{Students' responses to the scale questions in Table \ref{tab:likert}}
    \label{fig:likert}
    \vspace{-1em}
\end{figure}
